---
title: "Introduction to StatComp21074"
author: "Yuxin Zhang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp21074}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Overview

__StatComp21074__ is a simple Rpackage based on Zhu's research on network vector autoregression, which contains some simple functions to realize the numerical simulation in the paper.  

It is assumed that the node generation obeys the power-law distribution. According to the limitation of each parameter in the paper, functions such as _Z、W、statMu、statGamma、Y_ are segmented to achieve corresponding functions. _simudata_ is used to generate the simulated data, and _est_ is used to estimate the coefficients of the network autoregressive model.  

In this R package 'dPlyr' 'Plyr' 'Matrix' 'MASS' 'poweRlaw' will all be used.  


## simudata()

The source R code for _simudata_ is as follows: 

```{r,eval=FALSE}
#### Our function1 
simudata <- function(beta0, Beta, gamma0, Time, sig = 1, N, alpha) {
  W = W(N, alpha)
  p=length(gamma0)
  Z = Z(N, p)
  G = Beta[1]*W + Beta[2]*diag(nrow(W))
  mu = statMu(G, beta0 + Z %*% gamma0)
  Gamma0 = statGamma(G, sigma = sig)
  Y0 = mvrnorm(n = 1, mu = mu, Sigma = Gamma0)
  Ysim = Y(Y0 = Y0, beta0 + Z %*% gamma0, Beta, W, Time = Time)
  return(Ysim)
}
``` 


The built-in function W()、Z()、statMu()、statGamma()、Y() are also used in the generation of simulated data. Their R codes are shown below:  
  
Step 1: obtain network matrix W from power-law distribution  

```{r,eval=FALSE}
W <- function(N, alpha) {
  Numfollowers = rpldis(N, 1, alpha)  # generate random numbers for each nodes following power-law(1, alpha)
  A = sapply(Numfollowers, function(n) {
    # for node i, randomly select di nodes to follow it
    sel = rep(0, N)
    sel[sample(1:N, min(n, N))] = 1
    return(sel)
  })
  diag(A) = 0
  for (i in 1:N){
    if (sum(A[i,]) == 0)         # in case some row sums are zero
      A[i,sample(1:N,3)] = 1   # for those node, randomly select 3 followees
  }
  W = A / rowSums(A) # row-normalized adjacency matrix
  return(W)
} 
```  

Step 2: generate node-specific random vector Z  

```{r,eval=FALSE}
Z <- function(N, p, s = 0.5) {
  cov = diag(p)  # Set covariance matrix with the element of 0.5 ^ | i - j | 
  for (i in 1:(p-1)){
    for (j in (i+1):p){
      cov[i,j] = s^abs(i-j)
    }
  }
  cov = t(cov)+cov
  diag(cov)=1
  Z = mvrnorm(N, mu = rep(0,p), Sigma = cov) 
  return(Z)
}
```  

Step 3: generate simulation data  
step 3.1: We need to calculate the mean and covariance of the stationary state to sample the initial state Y0.  

```{r,eval=FALSE}
#using proposition1 and Case3 to obtain the mean and covariance matrix of stationary time series
statMu <- function(G, Beta0) {
  mu = solve(diag(length(Beta0)) - G) %*% Beta0  
  return(mu)
}
statGamma <- function(G, sigma) {
  Gamma0 = (diag(nrow(G)) + tcrossprod(G) + tcrossprod(G %*% G) + tcrossprod(G %*% G %*% G)) * sigma^2
  # Tayler expansion in case3
  return(Gamma0)
} 
```  

step3.2: function for simulationg Y series  

```{r,eval=FALSE}
Y <- function(Y0, Beta0, Beta, W, sig = 1, Time) {
  Ysim = matrix(0, nrow = length(Beta0), ncol = Time + 1)  # use Ysim to store the simulated data
  Ysim[, 1] = as.vector(Y0)  # the first column of Ysim holds Y0
  for (i in 1:Time) {
    Ysim[, i + 1] = as.vector(Beta0 + Beta[1] * W %*% Ysim[, i] + Beta[2] * 
                                Ysim[, i] + rnorm(length(Beta0), sd = sig))  # simulate
  }
  return(Ysim)
}
```  




## est()

The source R code for _est_ is as follows:  

```{r,eval=FALSE}
# The function requires the user to obtain simulated data 
# and then input it as a parameter to the est()
est <- function(Ysim, N, alpha, p){
  W = W(N, alpha)
  
  Z = Z(N, p)
  WY = W %*% Ysim  # WY
  Time = ncol(Ysim) - 1  # cause Ysim included Y0
  
  # Joining together the X
  int = rep(1, nrow(Ysim) * Time)
  self = as.vector(WY[, -ncol(Ysim)])
  other = as.vector(Ysim[, -ncol(Ysim)])
  realz = matrix(0, nrow = N*Time, ncol = p)
  for (i in seq(1, N*Time,N)){
    realz[i:(i+N-1),] = Z
  }
  
  X = as.matrix(bind_cols(int, self, other, realz))
  invXX = solve(crossprod(X)) 
  Y = as.vector(Ysim[, -1])  
  
  thetahat = invXX %*% t(X) %*% Y  # estimation equation (2.8)
  return(list(theta = thetahat))
}
```

In order to empirically use _simudata_ and _est_, one generates 30 observations of 50 nodes respectively. The R code for empirically use  _simudata_ and _est_ are as follows.

```{r}
library(dplyr)
library(plyr)
library(Matrix)
library(MASS)
library(poweRlaw)
library(StatComp21074)

N = 50  #numbers of nodes
alpha = 1.2  #parameter of power-law
Time = 30   #The length of time
gamma0 = c(-0.5,0.3,0.8,0,0) #fixed parameter of Z
p = length(gamma0)
beta0 = rep(0.3,N) #Intercept term coefficient
Beta = c(0.1,0.5)  #Regression coefficient
Ysim = simudata(beta0, Beta, gamma0, Time, sig = 1, N, alpha)
est(Ysim,N,alpha,p)
```

The above results show the estimate value of coefficients.




